\RequirePackage{luatex85}
\documentclass[eqno]{ltjsarticle}
\usepackage{luatexja-fontspec}
\usepackage[a4paper, top=25mm, bottom=25mm, left=25mm, right=25mm]{geometry}
\usepackage{luatexja} 
\usepackage{multicol,amsmath,amssymb,mathtools,ascmac,amsthm,amscd,physics,comment,dcolumn,titlesec,mathrsfs,test,tikz-cd,enumitem}
\usetikzlibrary{arrows.meta,calc}
\titleformat*{\section}{\Large\bfseries}
\setlength{\parindent}{0pt}
\usepackage[most]{tcolorbox}
\tikzset{every picture/.style={remember picture,baseline=(current bounding box.center)}}
\usetikzlibrary{decorations.pathmorphing}
%\everymath{\displaystyle}
\begin{document}
\title{三角圏上のBridgeland安定性条件}
\date{}
\author{大阪大学大学院理学研究科数学専攻\\山本　雄大}
\maketitle
\tableofcontents
\input{1triangulated_category}
\input{2fundamental_property_of_triangulated_category}
\input{3definition_of_derived_category}
\input{4properties_tri}
\input{5t_structure}
\input{6stability_conditions}
\input{7space_of_stability_conditions}
\input{8qgr}
\input{9GL}
\input{10matrix_factorization}

\begin{thebibliography}{99}

	\bibitem[Tod13]{Tod13}
	Yukinobu Toda
		\textit{Gepner type stability conditions on graded matrix factorizations},

	\bibitem[MMS09]{MMS09}
Emanuele Macri, Sukhendu Mehrotra, Paolo Stellari
		\textit{Inducing stability conditions},
	
	\bibitem[KS08]{KS08}
	Maxim Kontsevich, Yan Soibelman
		\textit{Stability structures, motivic Donaldson-Thomas invariants and cluster transformations},

	\bibitem[Bri07]{Bri07}
	Bridgeland, Tom,
		\textit{Stability conditions on triangulated categories},
	Annals of Mathematics, Vol. 166, No. 2, 2007, pp. 317–345.


	\bibitem[KST06]{KST06}
	Hiroshige Kajiura, Kyoji Saito, Atsushi Takahashi
		\textit{Matrix Factorizations and Representations of Quivers II: type ADE case},

	\bibitem[Tak05]{Tak05}
	 Atsushi Takahashi
		\textit{Matrix Factorizations and Representations of Quivers I},

	\bibitem[KS06]{KS06}
	Masaki Kashiwara and Pierre Schapira,
		\textit{Categories and Sheaves},
	Grundlehren der Mathematischen Wissenschaften, vol. 332,
	Springer-Verlag, Berlin, 2006.

	\bibitem[Kuz03]{Kuz03}
	\textit{Derived categories of cubic and V14 threefolds},

	\bibitem[GM03]{GM03}
	S. I. Gelfand and Yu. I. Manin,
	\textit{Methods of Homological Algebra}, 2nd ed.,
	Springer Monographs in Mathematics, Springer, 2003.

	\bibitem[AZ94]{AZ94}
	Michael Artin and James J. Zhang,
	\textit{Noncommutative Projective Schemes},
	Adv. Math. \textbf{109} (1994), no.~2, 228--287.

	\bibitem[BK89]{BK89}
	A.~Bondal and M.~Kapranov,
	\newblock Representable functors, Serre functors, and reconstructions,
	\newblock {\em Izv. Akad. Nauk SSSR Ser. Mat.} \textbf{53} (1989), no.~6, 1183--1205.
	\newblock English transl.: {\em Math. USSR Izv.} \textbf{35} (1990), no.~3, 519--541.

	\bibitem[Ri89]{Ri89}
	J.~Rickard,
	\newblock Morita theory for derived categories,
	\newblock {\em J. London Math. Soc. (2)} \textbf{39} (1989), no.~3, 436--456.


	\bibitem[GL87]{GL87}
	W.~Geigle and H.~Lenzing,
	\newblock A class of weighted projective curves arising in representation theory of finite-dimensional algebras,
	\newblock in *Singularities, Representation of Algebras, and Vector Bundles* (Lambrecht, 1985), Lecture Notes in Math. 1273, Springer, Berlin, 1987, pp. 265–297.
	
	\bibitem[BBD]{BBD}
	A. A. Beilinson, J. Bernstein, and P. Deligne,
	\textit{Faisceaux pervers},
	Astérisque, \textbf{100}, Société Mathématique de France, 1982. Chapitre 1.

	\bibitem[Gro57]{Gro57}
	A.~Grothendieck,
	\textit{Sur quelques points d'algèbre homologique},
	Tohoku Math. J. (2) \textbf{9} (1957), 119--221.

	\bibitem[Serre55]{Serre55}
	J.-P.~Serre,
	\newblock Faisceaux algébriques cohérents,
	\newblock \emph{Ann. of Math.} \textbf{61} (1955), 197--278.

\end{thebibliography}
\end{document}
